A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2018-03-12 analysis/paper/paper.Rmd
stray character in YAML
centre -> center

ggsave("../figures/plot_structured_data_files_per_file_tally.png",
       plot_structured_data_files_per_file_tally,
       width = 10)
```

@@

```{r datacite-plots}
datacentre_plot <-
  datacentre %>%
  mutate(Var1 = str_wrap(Var1, 20)) %>%
  slice(1:10) %>%
ggplot(aes(reorder(Var1, n),
           n)) +
  geom_col(fill = wes_palette("Rushmore1")[4]) +
  coord_flip() +
  xlab("Data centre") +
  ylab("") +
  theme_new() +
  theme(axis.text.y  = element_text(size = 8))

>>>>

ggsave("../figures/plot_structured_data_files_per_file_tally.png",
       plot_structured_data_files_per_file_tally,
       width = 10,
       height = 4)
```

@@

```{r datacite-plots}
datacentre_plot <-
  datacentre %>%
  mutate(Var1 = str_wrap(Var1, 20)) %>%
  slice(1:10) %>%
ggplot(aes(reorder(Var1, n),
           n)) +
  geom_col(fill = wes_palette("Rushmore1")[4]) +
  coord_flip() +
  xlab("Data center") +
  ylab("") +
  theme_new() +
  theme(axis.text.y  = element_text(size = 8))
